---
title: "Analyses"
author: "Brian W. Rolek"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
date: "28 April 2023"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

Contact author: brianrolek at gmail.com.

Supplemental materials for:
Larned, A. F., B. W. Rolek, K. Silaphone, S. Pruett, R. Bowman, B. Lohr. 2023. Habitat use and dynamics of an Endangered passerine, the Florida Grasshopper Sparrow (Ammodramus savannarum floridanus), after prescribed fires.

We used dynamic occupancy models that accounted for misclassifications and detection probability. We implemented Models in R and Bayesian software NIMBLE.  

# 1. Metadata
Metadata associated with the file "data\data-final.Rdata". Once loaded into R, this file contains the object "dat.conv", a list containing data for input into the JAGS model. Data fields include: 

+ Y = Observed states: 1 = no detection, 2 = uncertain detection, 3 = certain detection. A matrix of dimensions nsite x nvisit x nyear.
+ nsite = The number of sites surveyed at Avon Park and retained for analyses.
+ nvisit = The maximum number of survey visits within breeding seasons.
+ nyear = The total number of years of surveys. 
+ date = The date during each survey visit. A matrix of dimensions nsite x nvisit x nyear.
+ hr = Time after civil dawn during the start of each survey visit. A matrix of dimensions nsite x nvisit x nyear.

# 2. Basic Model Without Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//01-misclass_basic.R')
```
```{r, basic, eval=FALSE}
```

# 3. Global Detection Model Including All Covariates for Detection  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//02-misclass_global_detection.R')
```
```{r, global detection, eval=FALSE}
```

# 4. Bayesian latent indicator scale selection (BLISS) to Select Spatial Scales and Summary Statistics of Covariates  

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//03-misclass_BLISS.R')
```
```{r, BLISS, eval=FALSE}
```

# 5. Gibb's Variable Selection (GVS)

## 5.1. Calculate Prior Probabilities (step 1)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//04-model-probs-for-priors-GVS_step1.R')
```
```{r, prior probs, eval=FALSE}
```

## 5.2 Run Global Model to Obtain Estimates for Pseudopriors (step 2)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//05-misclass_GVS_step2.R')
```
```{r, global model, eval=FALSE}
```

## 5.3 Run Model with GVS (step 3)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R//06-misclass_GVS_step3.R')
```
```{r, gibbs variable selection, eval=FALSE}
```