---
title: "Analyses"
author: "Brian W. Rolek"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
date: "14 July 2022"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 16pt;
}
</style>
Supplemental materials for:
Larned, A. F., B. W. Rolek, K. Silaphone, S. Pruett, R. Bowman, B. Lohr. 2022. Habitat use and dynamics of an Endangered passerine, the Florida Grasshopper Sparrow (Ammodramus savannarum floridanus), after prescribed fires.

All analyses use occupancy models that account for misclassification and detection probability. Models were implemented in R and bayesian software NIMBLE.  

# 1. Basic Model Without Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('01-misclass_basic.R')
```
```{r, basic, eval=FALSE}
```

# 2. Global Detection Model Including All Covariates for Detection  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-misclass_global_detection.R')
```
```{r, global detection, eval=FALSE}
```

# 3. BLISS to Select Appropriate Spatial Scales and Summary Statistics  
Bayesian latent indicator scale selection (BLISS)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-misclass_BLISS.R')
```
```{r, BLISS, eval=FALSE}
```

# 4. Calculate Prior Probabilities for Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-model-probs-for-priors-GVS.R')
```
```{r, prior probs, eval=FALSE}
```

# 5. Run Global Model to Obtain Estimates for Gibbs Variable Selection (step 1)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-misclass_GVS_step1.R')
```
```{r, global model, eval=FALSE}
```

# 6. Run Model with Gibbs Variable Selection (step 2)
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('06-misclass_GVS_step2.R')
```
```{r, gibbs variable selection, eval=FALSE}
```