---
title: "Analyses"
author: "Brian W. Rolek"
date: "May 11, 2021"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 16pt;
}
</style>

# 1. Misclassification Model without Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('01-misclass_basic.R')
```
```{r, basic, eval=FALSE}
```

# 2. Misclassification Model Including All Covariates for Detection  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-misclass_global_detection.R')
```
```{r, global detection, eval=FALSE}
```

# 3. Misclassification Model with BLISS to Select Appropriate Spatial Scales and Summary Statistics 
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-misclass_BLISS.R')
```
```{r, BLISS, eval=FALSE}
```

# 4. Calculate Prior Probabilities for Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-model-probs-for-priors-GVS.R')
```
```{r, prior probs, eval=FALSE}
```

# 5. Run Global Misclassification Model for Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-misclass_GVS_step1.R')
```
```{r, global model, eval=FALSE}
```

# 6. Run Misclassification Model with Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('06-misclass_GVS_step2.R')
```
```{r, gibbs variable selection, eval=FALSE}
```